Community Embeddings for Friend Suggestions

### 2020-10-12 conference_101719.tex
add figure to p1
structure
extend citation

@@

Recommender systems are built on top of user-item interaction. Friend suggestions are a simpler type of recommender system. For friend suggestions, no distinction is made between users and items. The entity user is both the subject and object of recommendation. This results in a simple data model, which can be used for structural friend suggestions, as shown in Fig. \ref{fig:data_model}:

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node distance=6cm]
        \node (user) [user] {User};
        \path [arrow] (user) edge[loop right] node[right]{relate} (user);
    \end{tikzpicture}
    \caption{Minimal data model supporting friend suggestions.}
    \label{fig:data_model}
\end{figure}

@@

The hit-rate metric on top-$N$ recommendations provides a realistic option of evaluating recommender systems \cite{Cremonesi2010PerformanceOR, Palumbo2017entity2rec, Zhao2019ATS}.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{images/fb/graph_d4.png}
    \caption{\citetitle{social_circles_fb} graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$.\cite{networkx}}
    \label{fig:fb_graph}
\end{figure}

@@

Recommender systems are built on top of user-item interaction. Friend suggestions are a simpler type of recommender system. For friend suggestions, no distinction is made between users and items. The entity user is both the subject and object of recommendation. This results in a simple data model, which can be used for structural friend suggestions, as shown in Fig. \ref{fig:data_model}.

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[node distance=6cm]
        \node (user) [user] {User};
        \path [arrow] (user) edge[loop right] node[right]{relate} (user);
    \end{tikzpicture}
    \caption{Minimal data model supporting friend suggestions.}
    \label{fig:data_model}
\end{figure}

@@

The hit-rate metric on top-$N$ recommendations provides a realistic option of evaluating recommender systems and with the leave-one-out (LOO) strategy is used often in literature \cite{Cremonesi2010PerformanceOR, Palumbo2017entity2rec, Zhao2019ATS, He2017NeuralCF}.
